Enforced Invariant Confluence

### 2020-01-14 doc/the_vldb_journal_paper/sections/conclusion.tex
Added Peter Bailis to acks.

\textbf{Acknowledgments.}
The authors would like to thank Alan Fekete, Peter Alvaro, Alvin Cheung,
Alexandra Meliou, Anthony Tan, and Cristina Teodoropol for fruitful discussion
and feedback.
%
This research is supported in part by DHS Award HSHQDC-16-3-00083, NSF CISE
Expeditions Award CCF-1139158, and gifts from Alibaba, Amazon Web Services, Ant
Financial, CapitalOne, Ericsson, GE, Google, Huawei, Intel, IBM, Microsoft,
Scotiabank, Splunk and VMware.

>>>>

\textbf{Acknowledgments.}
The authors would like to thank Alan Fekete, Alexandra Meliou, Alvin Cheung,
Anthony Tan, Cristina Teodoropol Peter Alvaro, and Peter Bailis, for fruitful
discussion and feedback.
%
This research is supported in part by DHS Award HSHQDC-16-3-00083, NSF CISE
Expeditions Award CCF-1139158, and gifts from Alibaba, Amazon Web Services, Ant
Financial, CapitalOne, Ericsson, GE, Google, Huawei, Intel, IBM, Microsoft,
Scotiabank, Splunk and VMware.
